\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2023-03-05 Latex/paper-resum.tex
New version
Moving the proofs to the appendix

\usepackage{graphicx}
\graphicspath{{fig/}}
\usepackage{epstopdf}
\usepackage{booktabs}
\usepackage{multirow}

@@

\section{Preliminaries and notation}\label{sec:Notation}
Consider a continuous-time economy where zero-coupon bonds are traded for all maturities. The price at time $t$ of a zero-coupon bond with maturity $T$ is denoted by $P(t,T)$ where $0\leq t \leq T$. Clearly, $P(T,T)=1$. We define the compounded instantaneous forward rate forward rate as:
\begin{eqnarray*}
f(t,T)= -\partial_{T}\ln P(t,T)
\end{eqnarray*}
and the spot interest rates as:
\begin{eqnarray*}
r(t)=\lim_{T\longrightarrow t} -\partial_{T}\ln P(t,T).
\end{eqnarray*}
We have that the price of a zero-coupon bond is given by
\begin{eqnarray*}
P(t,T)=\exp\left(-\int^{T}_{t} f(t,u) du\right).
\end{eqnarray*}

Before the financial crisis, there was a single curve framework where there was a single curve for discounting and forecasting. Since then, the market has adopted a multi-curve approach with two different curves: the discounting curve and the estimation curve chosen based on the maturity of the underlying rate. The difference between these two curves is known as basis. In this paper, we will assume that the basis are not stochastic. Therefore can be directly obtained from the market at time $t=0$. In other words, the estimation forward curve $f_{E}(t, T)$ is given by
\begin{equation}\label{estimation_forward_rate_curve}
f_{E}(t,T) = f_{ois}(t,T) + s(t,T)
\end{equation}
where and $f_{ois}$ is the discount curve and $s(t,T)$ are the basis between the two curves, i.e. $s(t,T)= f_{E}(0,T) - f_{ois}(0,T)$.\\

We will assume that the $f_{ois}$ dynamics follows a single factor Heath-Jarrow-Morton model under the $\mathbb{Q}$-measure. Therefore, let $T>0$ a fixed time horizon, $t>0$ the starting time, and $W$ a Brownian motion defined on a complete probability space $(\omega, \mathcal{F}, \mathbb{P})$. Then, under the HJM we have the following dynamics
\begin{align}\label{ois_forward_rate_curve}
df_{ois}(t,T) &= \sigma(t,T)\nu(t,T)dt + \sigma(t,T)dW^{\mathbb{Q}}_t
\end{align}
where $\nu(t,T)=\int_{t}^{T}\sigma(t,s)ds$ and $\sigma(t, T)$ are $\mathcal{F}_{t}$-adapted process that are positive functions for all $t,T$ . In particular, we have that
\begin{eqnarray*}
f_{ois}(t,T)= -\partial_{T}\ln P_{ois}(t,T).
\end{eqnarray*}

In order to have a Markovian representation of the HJM, we will assume that the volatility is separable, i.e.
\begin{equation}
\sigma(t,T)= h(t)g(T).
\end{equation}
with $g$ a positive time-dependent function and $h$ a non-negative process. In addition
\begin{align*}
\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
k_t &= - \frac{\partial_t g(t)}{g(t)}.
\end{align*}
Throught this paper, we assume the following hypotheses on $\eta(t,x,y)$.
\begin{hypothesis}\label{boundedness_volatility} 
The process $\eta_t$ is global Lipschitz and differentiable a.s. In addition, we will suppose that
\begin{align*}
\alpha_1 \leq \eta(t,x,y) \leq \alpha_2 \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+}. \\
|\eta(t,x_2,y_2) - \eta(t,x_1,y_1)| \leq C_{x,y} \lVert (x_2-x_1,y_2-y_1)\rVert \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} 
\end{align*}
with $\lVert \cdot \rVert$ euclidean norm in $\mathbb{R}^{2}$.
\end{hypothesis}
\begin{hypothesis}\label{boundedness_reversion} 
The mean reversion function $k(\cdot)$ is a continuous and positive a.s such that
\begin{equation*}
m_k < k(t) \leq M_k \quad \forall t \geq 0.
\end{equation*}

\begin{remark}
Under these assumptions on $k(\cdot)$, we have that
\begin{equation*}
\lim_{t \to \infty}  I(\alpha,0,t):= \lim_{t \to \infty} \int_{0}^{t} \exp\left(-\alpha \int_{u}^{t} k(s) ds\right) du \leq \frac{1}{\alpha m_k} \quad \text{with} \quad \alpha > 0.
\end{equation*}
On other hand, as well it is easy to show that
\begin{equation*}
\lim_{t \to \infty}  J(\alpha,0,t):= \lim_{t \to \infty} \int_{0}^{t} G^{\alpha}(u,t) \exp\left(-\alpha \int_{u}^{t} k(s) ds\right) du \leq \frac{1}{\alpha m^{\alpha+1}_{k}}
\end{equation*}
\end{remark}

\end{hypothesis}
\begin{remark}
Notice that the above hypotheses have been chosen for the sake of simplicity, but they can be replaced by adequate integrability conditions.
\end{remark}
We must note, that under the hypothesis (\ref{boundedness_volatility}) $\partial_x \eta(t,x,y)$ and $\partial_y \eta(t,x,y)$ are bounded. This version of the HJM is also known as the Cheyette model, \cite{Cheyette}. It is easy to show (see \cite{Andreasen01} that
\begin{equation}
r_{ois}(t)=f_{ois}(t,t)= f_{ois}(0,t) + x_t,
\end{equation}  
where
\begin{align}\label{short_rate_cheyette}
dx_t &= (-k_t x_t + y_t)dt + \eta(t,x_t,y_t) dW_t^{\mathbb{Q}} \nonumber \\
dy_t &= (\eta^{2}_t - 2 k_t y_t) dt ,
\end{align} 
with 
\begin{align*}
\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
k_t &= - \frac{\partial_t g(t)}{g(t)}.
\end{align*}
Now if we do a little bit of algebra and we use Itô formula we can show the next representation formula for $P_{ois}(t,T)$
\begin{equation}\label{bond_ois}
P_{ois}(t,T) = \frac{P_{ois}(0,T)}{P_{ois}(0,t)} \exp\left(-G(t,T)x_t - \frac{1}{2} G^{2}(t,T)y_t \right)
\end{equation}
where $G(t,T) = \int_{t}^{T} \exp\left(-\int_{t}^{u} k_s ds \right) du$. We must observe, that under the representation (\ref{estimation_forward_rate_curve}) we have that
\begin{equation}\label{bond_forward}
P_{E}(t,T)=H(t,T)P_{ois}(t,T)
\end{equation}
where $H(t,T)=\exp\left(-\int_{t}^{T}s(t,u) du \right)$.

\section{Basic introduction to Malliavin calculus}\label{sec:Malliavin}
Malliavin calculus is an infinite-dimensional calculus in a Gaussian space, that is, a stochastic calculus of variations. In other words, this is a theory that provides a way to calculate the derivatives of random variables defined in a Gaussian probability space with respect to the underlying noise. The initial objective of Malliavin was the study of the existence of densities of Wiener functionals such as solutions of stochastic differential equations. But, nowadays, it has become an important tool in stochastic analysis due to the increase in its applications. Some of these applications include stochastic calculus for fractional Brownian motion, central limit theorems for multiple stochastic integrals, and an extension of the Itô formula for anticipative processes, but especially mathematical finance. For example, we can apply Mallaivin calculus for computing hedging strategies, Greeks, or obtain price approximations. See, for example, \cite{AlosLorite} or \cite{Nualart} for more general content.\\

In our case, we are interested in using the Malliavin calculus to apply the Clark–Ocone representation theorem. But, first of all, let's introduce some basic concepts.\\

Now, we introduce the derivative operator in the Malliavin calculus sense and the divergence operator to establish the notation that we use in the remainder of the paper.\\

Consider $W=\left\{W_{t}, t\in \left[0,T\right]\right\}$ a Brownian motion defined on a complete probability space $\left(\Omega, \mathcal{F}, \mathbb{P}\right)$. Let $H=L^{2}(\left[0,T\right])$ and denote by 
\begin{eqnarray*}
W_{t} := \int^{T}_{0} t_{s} \d W_{s},
\end{eqnarray*}
the It\^o integral of a deterministic function $h \in H$, also known as Wiener integral. Let $\mathcal{S}$ be the set of smooth random variables of the form
\begin{eqnarray*}
F=f\left(W_{t_{1}}, \ldots, W{t_{n}}\right)
\end{eqnarray*}
with $t_{1}, \ldots, t_{n} \in \left[0,T\right]$ and $f$ is infinitely differentiable bounded function.

\medbreak

The derivative of a random variable $F$, $D_{s}F$, is defined as the stochastic process given by
\begin{eqnarray*}
D_{s}F = \sum^{n}_{i=1} \frac{\partial f}{\partial x_{i}}\left(W_{t_{1}}, \ldots, W_{t_{n}}\right)1_{\left[0, t_{j}\right]}(s), \hspace{0.4cm} s \in \left[0,T\right].
\end{eqnarray*}

The iterated derivative operator of a random variable $F$ is defined by
\begin{eqnarray*}
D^{m}_{s_{1}, \ldots, s_{m}} F = D_{s_{1}} \cdots D_{s_{m}}F, \hspace{0.4cm} s_{1}, \ldots, s_{m} \in \left[0,T\right].
\end{eqnarray*}

\cite{Nualart} stated that these operators are closable from $L^{p}(\Omega)$ into $L^{p}(\Omega; L^{2}\left[0,T\right])$ for any $p\geq1$, and we denote by $\mathbb{D}^{n,p}$ the closure of $\mathcal{S}$ with respect to the norm
\begin{eqnarray*}
\left\|F\right\|_{n,p} := \left(E\left[F\right]^{p} + \sum^{n}_{i=1} E\left\|D^{i} F\right\|^{p}_{L^{2}\left(\left[0,T\right]^{i}\right)} \right)^{\frac{1}{p}}.
\end{eqnarray*}

\medbreak

We define $\delta$ as the adjoint of derivative operator $D$, also referred to as the Skorohod integral. The domain of $\delta$, denoted by $Dom\text{ }\delta$, is the set of elements $u \in L^{2}([0,T] \times \Omega)$ such that there exists $\delta(u) \in L^{2}(\Omega)$ satisfying the duality relation
\begin{eqnarray*}
E\left[\delta(u) F \right] = E\left[\int^{T}_{0} \left(D_{s} F\right) u_{s} \d s\right].
\end{eqnarray*}

The operator $\delta$ is an extension of the Itô integral in the sense that the set $L^{2}_{a}([0,T] \times \Omega)$ of square integrable and adapted processes is included in $Dom\text{ }\delta$ and the operator $\delta$ restricted to $L^{2}_{a}([0,T] \times \Omega)$ coincides with the Itô stochastic integral.

\medbreak

For any $u \in Dom\text{ }\delta$, we will use the following notation
\begin{eqnarray*}
\delta(u)=\int^{T}_{0}u_{s}\d W_{s}.
\end{eqnarray*}

\medbreak

The representation of functionals of Brownian motion by stochastic integrals, also known as martingale representation, has been widely studied over the years. It states that if $F$ is a square-integrable random variable, there exists a unique adapted process $\varphi$ in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$ such that
\begin{eqnarray*}
F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} \varphi^{i}_{s} dW^{i}_{s}.
\end{eqnarray*}
In other words, there exists a unique martingale representation or, more precisely, the integrand $\varphi$ in the representation exists and is unique in $L^{2}(\Omega \times \left[0,T\right]; \mathbb{R}^{d})$.

\medbreak

Unfortunately, it is not easy to find an analytic representation of the process $\varphi$. Here, the Malliavin calculus helps us to find a solution. When the random variable $F$ is Malliavin differentiable, the process $\varphi$ appearing in It\^o's representation theorem, is given by
\begin{eqnarray*}
\varphi^{i}=E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right].
\end{eqnarray*}
In fact,
\begin{eqnarray}\label{clark-okone}
F=E\left[F\right] + \sum^{n}_{i=1}\int^{T}_{0} E\left[D^{W^{i}}_{t}F|\mathcal{F}^{W}_{s}\right] dW^{i}_{s}
\end{eqnarray}
is the Clark-Ocone representation formula.

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula . In order to introduce a general idea of the method. Let define a $Z_t = f(x_t)$. Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$. Then, if we use the Clark-Ocone representation, we have that
\begin{equation*}
f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left(f(x_t)\right) + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) dW^{\mathbb{Q}_1}_s
\end{equation*}
Now, if we take $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and we use the Girsanov's theorem, we get that
\begin{equation}\label{general_convexity}
\mathbb{E}^{\mathbb{Q}_2}\left( f(x_t) \right) = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left(\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) \lambda_s ds \right). 
\end{equation}
The second term, is the convexity adjustment to due to change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$. The differents choice of $f$, $\mathbb{Q}_1$ and $\mathbb{Q}_2$ will allow us to get an approximation of the convexity adjustment for the different case of interest. 
\subsection{FRAs Vs futures}
 The cash flows in FRAs and futures are computed under different measures. Consequently, we need to adjust the futures price quote to transform them into FRAs price quotes. As usual, we will define the forward rate at time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as:
\begin{equation}\label{forward_rate}
L_{E}(t_0, t_1, t_2) = \frac{\left(\frac{P_{E}(t_0,t_1)}{P_{E}(t_0,t_2)} - 1 \right)}{\delta_{t_1,t_2}}
\end{equation} 
where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$. Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$. Let us define the future rate as:    
\begin{equation}\label{future}
\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left(L_{E}(t_0, t_1, t_2) \right), 
\end{equation}
where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is:
\begin{equation*}
CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left(L_{E}(t_0, t_1, t_2) \right).
\end{equation*}
From (\ref{ois_forward_rate_curve}) and since $f_{ois}(t,T)$ is a $\mathbb{Q}^{T}$ martingale, we have that
\begin{equation}\label{girsanov_spot_forward}
dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,t_2) dt. 
\end{equation}
Now, if we use (\ref{general_convexity}) with $f(x_t)=L_{E}(t,t_0, t_1, t_2)$, $\mathbb{Q}_1=\mathbb{Q}$, $\mathbb{Q}_1=\mathbb{Q}^{t_2}$ and $\lambda_t = \nu(t,t_2)$,  we get that
\begin{equation}\label{ca_general_future}
CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left(\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\left(D_s L_{E}(t_0,t_1,t_2) \right) \nu(s,t_2) ds \right)
\end{equation}
where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Now, from the definition of $L_{E}(t,T)$. Now, if we calculate the malliavin derive of $L_{E}(t_0,t_1,t_2)$ we have that
\begin{equation*}
D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) 
\end{equation*}
Now from the zero coupon representation formula (\ref{bond_ois}) we get that
\begin{equation*}
D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) = \frac{\left(\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) \right)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}
\end{equation*}
therefore

>>>>

\usepackage{graphicx}
\graphicspath{{fig/}}
\usepackage{epstopdf}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{float}

@@

\section{Preliminaries and notation}\label{sec:Notation}
In this section, we give the basic preliminaries and notation necessary throughout the paper.
\subsection{A tale of two curves}
Consider a continuous-time economy where zero-coupon bonds are traded for all maturities. The price at time $t$ of a zero-coupon bond with maturity $T$ is denoted by $P(t,T)$ where $0\leq t \leq T$. Clearly, $P(T,T)=1$. The compounded instantaneous forward rate is defined as:
\begin{eqnarray*}
f(t,T)= -\partial_{T}\ln P(t,T)
\end{eqnarray*}
and the spot interest rates as:
\begin{eqnarray*}
r(t)=\lim_{T\longrightarrow t} -\partial_{T}\ln P(t,T).
\end{eqnarray*}
Therefore, the zero-coupon bond price is given by
\begin{eqnarray*}
P(t,T)=\exp\left(-\int^{T}_{t} f(t,u) du\right).
\end{eqnarray*}

Before the financial crisis, there was a single curve framework based on the same curve for discounting and forecasting. Since then, the market has adopted a multi-curve approach with two different curves: the discount curve and the estimation curve chosen based on the maturity of the underlying rate. The difference between these two curves is known as the basis. In this paper, we will assume that the basis are not stochastic. Therefore, it can be obtained directly from the market at time $t=0$. In other words, the estimation forward curve $f_{E}(t, T)$ is given by
\begin{equation}\label{estimation_forward_rate_curve}
f_{E}(t,T) = f_{ois}(t,T) + s(t,T)
\end{equation}
where and $f_{ois}$ is the discount curve and $s(t,T)$ are the basis between the two curves, i.e. $s(t,T)= f_{E}(0,T) - f_{ois}(0,T)$.\\

Given the discount curve $P_{ois}(t,T)$ and using the representation \eqref{estimation_forward_rate_curve}, it is possible to find the discount curve for the estimation curve using the relation
\begin{equation}\label{bond_forward}
P_{E}(t,T)=H(t,T)P_{ois}(t,T)
\end{equation}
where $H(t,T)=\exp\left(-\int_{t}^{T}s(t,u) du \right)$.

\subsection{The model}
We will assume that the $f_{ois}$ dynamics follows a single factor Heath-Jarrow-Morton model under the $\mathbb{Q}$-measure. Therefore, let $T>0$ a fixed time horizon, $t>0$ the starting time, and $W$ a Brownian motion defined on a complete probability space $(\omega, \mathcal{F}, \mathbb{P})$. Then, the HJM model is defined by
\begin{align}\label{ois_forward_rate_curve}
df_{ois}(t,T) &= \sigma(t,T)\nu(t,T)dt + \sigma(t,T)dW^{\mathbb{Q}}_t
\end{align}
where $\nu(t,T)=\int_{t}^{T}\sigma(t,s)ds$ and $\sigma(t, T)$ are $\mathcal{F}_{t}$-adapted process that are positive functions for all $t,T$. In particular, we have that
\begin{eqnarray*}
f_{ois}(t,T)= -\partial_{T}\ln P_{ois}(t,T).
\end{eqnarray*}

To have a Markovian representation of the HJM, we will assume that the volatility is separable, i.e.
\begin{equation}\label{separation_condition}
\sigma(t,T)= h(t)g(T).
\end{equation}
with $g$ a positive time-dependent function and $h$ a non-negative process. In addition,
\begin{align*}
\eta_t &= g(t)h(t,x_t,y_t)  \nonumber \\
k_t &= - \frac{\partial_t g(t)}{g(t)}.
\end{align*}

This version of the HJM is also known as the Cheyette model, \cite{Cheyette}. In \cite{AndreasenPiterbarg}, we have the following proposition.
\begin{proposition}
Consider the HJM model \eqref{ois_forward_rate_curve} with the separable volatility condition \eqref{separation_condition}. Define the stochastic processes $x(t)$ and $y(t)$ by
\begin{align}\label{short_rate_cheyette}
dx_t &= \left(-k(t) x(t) + y(t)\right)dt + \eta\left(t,x(t),y(t)\right) dW_t^{\mathbb{Q}} \nonumber \\
dy_t &= \left(\eta^{2}(t) - 2 k(t) y(t)\right) dt ,\nonumber \\
x(0) &=y(0)=0.
\end{align}
All zero-discount bonds are deterministic functions of the processes $x(t)$ and $y(t)$,
\begin{eqnarray*}
P_{ois}(t,T)=P(t, T, x(t), y(t)), 
\end{eqnarray*}
where 
\begin{eqnarray}\label{bond_ois}
P_{ois}(t,T,x,y) = \frac{P_{ois}(0,T)}{P_{ois}(0,t)} \exp\left(-G(t,T)x - \frac{1}{2} G^{2}(t,T)y \right),
\end{eqnarray}
where $G(t,T) = \int_{t}^{T} \exp\left(-\int_{t}^{u} k(s) ds \right) du$ and the short rate is
\begin{equation}
r_{ois}(t)=f_{ois}(t,t)= f_{ois}(0,t) + x(t).
\end{equation} 
\end{proposition}

The whole interest rate curve can be reduced to the evolution of the two-state variables $x(t)$ and $y(t)$. The variable $x(t)$ constitutes the main yield curve driver, whereas $y(t)$ is an auxiliary `convexity' variable. Note that the function $y(t)$ is not deterministic, however, it does not have a diffusion term. We call such processes locally deterministic. \\

We can see from \eqref{short_rate_cheyette} that
\begin{equation*}
x(t_a) = \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) y(u) du + \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,x(u),y(u)) dW_u^{\mathbb{Q}}. 
\end{equation*}

In order to have a more manageable model, we will follow the ideas of \cite{AndreasenPiterbarg} where the state variables are approximated. So, we can approximate $y(t)$ as
\begin{equation}\label{approximation_y_t}
y(t) \approx \bar{y}(t):=\int_{0}^{t} \exp\left(-2\int_{u}^{t} k(w) dw \right) \eta^{2}(u,x(0),y(0)) du
\end{equation} 
and
\begin{eqnarray}
X_{t_a} \approx \bar{X}(t_a):= \bar{x}_0(t_a)  &+& \int_{0}^{t_a} \exp\left(-\int_{s}^{t_a}k(u) du\right) \bar{y}(u) du \nonumber \\
&+& \int_{0}^{t_a}  \exp\left(-\int_{s}^{t_a}k(u) du \right) \eta(u,\bar{x}(u),\bar{y}(u)) dW_u^{\mathbb{Q}}   \label{approximation_x_t_a}
\end{eqnarray}
with initial condition $\bar{x}_{0}(t_a)$ is such a way that  
\begin{equation*}
S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_{t_a}) = S_{a,b}(0).
\end{equation*}

\subsection{Model constraints}
To calculate the convergence order of the convexity adjustment approximation, we use the following hypotheses on $\eta(t,x,y)$.
\begin{hypothesis}\label{boundedness_volatility} 
The process $\eta_t$ is global Lipschitz and differentiable a.s. In addition, we will suppose that
\begin{align*}
\alpha_1 \leq \eta(t,x,y) \leq \alpha_2 \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+}. \\
|\eta(t,x_2,y_2) - \eta(t,x_1,y_1)| \leq C_{x,y} \lVert (x_2-x_1,y_2-y_1)\rVert \quad \forall (t,x,y) \in \mathbb{R}^{+} \times \mathbb{R} \times \mathbb{R}^{+} 
\end{align*}
with $\lVert \cdot \rVert$ euclidean norm in $\mathbb{R}^{2}$.
\end{hypothesis}

The mean reversion function $k(\cdot)$ influences the range and flexibility of the volatility structure. The function is always positive and, in practice, it is usually low.

\begin{hypothesis}\label{boundedness_reversion} 
The mean reversion function $k(\cdot)$ is a continuous and positive a.s such that
\begin{equation*}
m_k < k(t) \leq M_k \quad \forall t \geq 0.
\end{equation*}

As a consequence.
\begin{remark}
Under these assumptions on $k(\cdot)$, we have that
\begin{equation*}
\lim_{t \to \infty}  I(\alpha,0,t):= \lim_{t \to \infty} \int_{0}^{t} \exp\left(-\alpha \int_{u}^{t} k(s) ds\right) du \leq \frac{1}{\alpha m_k} \quad \text{with} \quad \alpha > 0.
\end{equation*}
On other hand, 
\begin{equation*}
\lim_{t \to \infty}  J(\alpha,0,t):= \lim_{t \to \infty} \int_{0}^{t} G^{\alpha}(u,t) \exp\left(-\alpha \int_{u}^{t} k(s) ds\right) du \leq \frac{1}{\alpha m^{\alpha+1}_{k}}
\end{equation*}
\end{remark}
\end{hypothesis}

The hypotheses have been chosen for simplicity, but they can be replaced by suitable integrability conditions.\\

Note, that under the hypothesis \eqref{boundedness_volatility}, $\partial_x \eta(t,x,y)$ and $\partial_y \eta(t,x,y)$ are bounded.

\subsection{Notation}
\textcolor{red}{(Falta pasteleo)}\\
$\delta_{t_1,t_2}=t_2 -t_1$ is the year fraction between $t_1$ and $t_2$.

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a general representation formula . In order to introduce a general idea of the method. Let define a $Z_t = f(x_t)$. Now, we suppose that $Z_t$ is martingale under the measure $\mathbb{Q}_1$ and that we want to compute $\mathbb{E}^{\mathbb{Q}_2}\left(Z_T \right)$, where $\mathbb{Q}_2$ is a measure such that $dW^{\mathbb{Q}_1}_t = dW^{\mathbb{Q}_2}_t +\lambda_t dt$. Then, if we use the Clark-Ocone representation, we have that
\begin{equation*}
f(x_t) = \mathbb{E}^{\mathbb{Q}_1}\left(f(x_t)\right) + \int_{0}^{t} \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) dW^{\mathbb{Q}_1}_s
\end{equation*}
Now, if we take $\mathbb{E}^{\mathbb{Q}_2}\left( \cdot \right)$ in the previous expression and we use the Girsanov's theorem, we get that
\begin{equation}\label{general_convexity}
\mathbb{E}^{\mathbb{Q}_2}\left( f(x_t) \right) = f(x_0) + \mathbb{E}^{\mathbb{Q}_1} \left(\int_{0}^{t}  \mathbb{E}^{\mathbb{Q}_1}_s\left( f^{\prime}(x_t) D_s x_t  \right) \lambda_s ds \right). 
\end{equation}
The second term, is the convexity adjustment to due to change of measure from $\mathbb{Q}_1$ to $\mathbb{Q}_2$. The differents choice of $f$, $\mathbb{Q}_1$ and $\mathbb{Q}_2$ will allow us to get an approximation of the convexity adjustment for the different case of interest. 
\subsection{FRAs Vs futures}
 The cash flows in FRAs and futures are computed under different measures. Consequently, we need to adjust the futures price quote to transform them into FRAs price quotes. As usual, we will define the forward rate at time $t_0$ between $t_1$ and $t_2$ under the forward curve $E$ as:
\begin{equation}\label{forward_rate}
L_{E}(t_0, t_1, t_2) = \frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1)}{P_{E}(t_0,t_2)} - 1 \right)
\end{equation} 
where $P_{E}(t,T)$ is the discount factor for the curve $E$ from $t$ to $T$, and $\delta_{t_1,t_2}$ is the year fraction between $t_1$ and $t_2$.

\begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for futures is 
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) \approx \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,x_0,\hat{y}_s) \nu(s,t_2) ds. 
\end{equation}
with 
\begin{equation*}
\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k_u du \right) \eta(u,x,y).
\end{equation*}
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_futures}.
\end{proof}

\begin{example}[Convexity adjustment for futures under the Hull-White model]\label{example_ca_future}
The Cheyette model can be reduced to Hull-White model using the following parameters
\begin{align*}
g(T) &= \exp(-kT), \\
h(t) &= \sigma.
\end{align*}
Moreover, from the definition of $g(\cdot)$ and $h(\cdot)$, we have that
\begin{align*}
\eta_s &= \sigma \exp(-ks),\\
\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-ku),\\
\nu(s,t_2) &= \sigma \frac{\exp(-ks) - \exp(-kt_2)}{k}.
\end{align*}
Then the convexity adjustment \eqref{ca_approximation_futures} is
\begin{align*}
CA(t_0,t_1) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}

In the Figure \ref{fig:Futures}, we can check the accuracy of the last formula versus Monte Carlo. The parameters that we have used are $\sigma=0.015$, $k=0.003$ and flat curve with level $r=0.01$.

\begin{figure}[H]
	\begin{center}
		\includegraphics[scale=0.3]{Figures/future_convexity.jpg}
	\end{center}
	\caption{Convexity Mc Vs Convexity Malliavin}
	\label{fig:Futures}
\end{figure} 
\end{example}

\subsection{OIS futures}
In this section, we will derive the convexity adjustment for the overnight-indexed swap, also known as OIS. Given $t_0 < t_1$, we define \textcolor{red}{(qué es R y Ravg, tipo OIS y tipo OIS medio, nombre tecnico?)}
\begin{align*}
R(t_0,t_1) &:=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right), \\
R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
\end{align*}
We observe that $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictable and are only observable in $t_1$. However, 
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$. Therefore, we can consider that the expected value under the measure $\mathbb{Q}$ is observable during entire period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales:
\begin{align*} 
\bar{R}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left( R(t_0,t_1)  \right), \\
\bar{R}_{avg}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left( R_{avg}(t_0,t_1)  \right).
\end{align*}

Given $t_0\leq t_1$, we define \textcolor{red}{(qué es I, buscar nombre chulo)}
\begin{equation*}
I(t_0,t_1) := \int_{t_0}^{t_1} r_s ds.
\end{equation*}

\begin{theorem}\label{Th_CA_OIS}[Convexity Adjustment approximation for OIS Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for OIS futures is 
\begin{equation}\label{convexity_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \approx \frac{\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right)\right)\exp\left(-\int_{t}^{t_1}\frac{\Gamma^{2}(s,t_0,t_1)}{2} ds\right) - 1}{\delta_{t_0,t_1}}
\end{equation}
and for the average OIS future is
\begin{equation}\label{convexity_avg_ois_future}
\mathbb{E}_t^{\mathbb{Q}}\left(R_{avg}(t_0,t_1)\right) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left(I(t_0,t_1)\right) }{\delta_{t_0,t_1}} \approx \frac{\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left(R(t_0,t_1)\right) \right)}{\delta_{t_0,t_1}} - \frac{\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds}{2\delta_{t_0,t_1}}
\end{equation}
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_OIS_futures}.
\end{proof}
